\textbf{ Interpretable Gaussian Processes for Stellar Light Curves }

### 2020-11-13 tex/gitlinks.tex
fixed typos in paper; more text

\newcommand{\codelink}[1]{\href{https://github.com/rodluger/starry_process/blob/3c024c44d780c51442e91d488e120a8eb4a05da5/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/rodluger/starry_process/blob/3c024c44d780c51442e91d488e120a8eb4a05da5/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/rodluger/starry_process/blob/3c024c44d780c51442e91d488e120a8eb4a05da5/tex/tests/#1.py}{\raisebox{-0.1em}{\input{tests/#1.tex}}}}
\newcommand{\cilink}[1]{\href{https://dev.azure.com/rodluger/starry_process/_build}{#1}}

>>>>

\newcommand{\codelink}[1]{\href{https://github.com/rodluger/starry_process/blob/150c31cb799f4eb003031cfb856cd3b53ab5f5fc/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/rodluger/starry_process/blob/150c31cb799f4eb003031cfb856cd3b53ab5f5fc/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/rodluger/starry_process/blob/150c31cb799f4eb003031cfb856cd3b53ab5f5fc/tex/tests/#1.py}{\raisebox{-0.1em}{\input{tests/#1.tex}}}}
\newcommand{\cilink}[1]{\href{https://dev.azure.com/rodluger/starry_process/_build}{#1}}

### 2020-11-13 tex/ms.tex
fixed typos in paper; more text

    \mathbf{E}_r^\top \,

@@

    \mathbf{E}_\phi^\top \,

@@

    \mathbf{E}_\lambda^\top \,

@@

\subsection{Probability density function}
%
For simplicity, we will adopt a uniform probability distribution for the
spot radius, characterized by a mean radius $r_0$ and a half-width $\Delta$:
%
\begin{align}
    p(r \, \big| \, \pmb{\theta}_{r})
    &=
    \begin{cases}
        \frac{1}{2\Delta} & r_0 - \Delta \leq r \leq r_0 + \Delta
        \\
        0 & \mathrm{otherwise}
        \quad,
    \end{cases}
\end{align}
%
where the hyperparameters of the distribution are
%
\begin{align}
    \pmb{\theta}_r = \left(
    r_0 \, \, \, \,
    \Delta \right)^\top
    \quad.
\end{align}
%
As we argue in the text, in practice it is often difficult to constrain the 
moments of the radius distribution above the first (the mean). It is 
therefore useful to also consider the limiting case of the radius distribution
as $\Delta \rightarrow 0$, in which case the PDF becomes
%
\begin{align}
    p(r \, \big| \, \pmb{\theta}_{r}, \Delta = 0)
    &=
    \delta(r - r_0)
    \quad,
\end{align}
%
where $\delta$ is the delta function.
%

\subsection{First moment}
%
The first moment of the radius distribution is (Equation~\ref{eq:e1})
%
\begin{align}
    \mathbf{e}_r
     & \equiv
    \int
    \mathbf{s}(r) \,
    p(r \, \big| \, \pmb{\theta}_{r}) \,
    \mathrm{d}r
    \nonumber \\
    &=
    \frac{1}{2\Delta}
    \int_{r_0 - \Delta}^{r_0 + \Delta}
    \mathbf{s}(r) \,
    \mathrm{d}r
    \quad.
\end{align}
%
Using the equations from the previous section, its components may be written
%
\begin{align}
    (e_r)^l_m
    &=
    \frac{\delta_{m,0}}{2\Delta}
    \int_{r_0 - \Delta}^{r_0 + \Delta}
    \tilde{s}_{l}(r) \,
    \mathrm{d}r
    \nonumber \\
    &=
    \frac{\delta_{m,0}}{2\Delta}
    \sum_{k=0}^{K-1} B^+_{l,k}
    \int_{r_0 - \Delta}^{r_0 + \Delta}
    b_{k}(r)
    \mathrm{d}r
    \nonumber \\
    &=
    \frac{\delta_{m,0} s}{2\Delta}
    \sum_{k=0}^{K-1} B^+_{l,k}
    \ln 
    \left(
        \frac{
            1+\exp\left(\frac{r -\Delta -\vartheta_k}{s}\right)
        }
        {
            1+\exp\left(\frac{r + \Delta -\vartheta_k}{s}\right)
        }
    \right)
    \quad.
\end{align}
%
In the limit $\Delta \rightarrow 0$,
%
\begin{align}
    \lim_{\Delta \rightarrow 0}
    \mathbf{e}_r
    &=
    \mathbf{B}^+ \mathbf{b}(r)
    \quad.
\end{align}
%

\subsection{Second moment}
%
The second moment of the radius distribution is (Equation~\ref{eq:E1})
%
\begin{align}
    \mathbf{E}_r
     & \equiv
    \int
    \mathbf{s}(r) \,
    \mathbf{s}^\top(r) \,
    p(r \, \big| \, \pmb{\theta}_{r}) \,
    \mathrm{d}r
    \nonumber \\
    &=
    \frac{1}{2\Delta}
    \int_{r_0 - \Delta}^{r_0 + \Delta}
    \mathbf{s}(r) \,
    \mathbf{s}^\top(r) \,
    \mathrm{d}r
    \quad.
\end{align}
%
As before, its components may be written
%
%
\begin{align}
    (E_r)^{l,l'}_{m,m'}
    &=
    \frac{\delta_{m,0}\delta_{m',0}}{2\Delta}
    \int_{r_0 - \Delta}^{r_0 + \Delta}
    \tilde{s}^l_{m}(r) \,
    \tilde{s}^{l'}_{m'}(r) \,
    \mathrm{d}r
    \nonumber \\
    &=
    \frac{\delta_{m,0}\delta_{m',0}}{2\Delta}
    \sum_{k=0}^{K-1} B^+_{l,k}
    \sum_{k'=0}^{K-1} B^+_{l',k'}
    \int_{r_0 - \Delta}^{r_0 + \Delta}
    b_{k}(r)
    b_{k'}(r)
    \mathrm{d}r
    \nonumber \\
    &= 
    \frac{\delta_{m,0}\delta_{m',0}s}{2\Delta}
    \sum_{k=0}^{K-1} B^+_{l,k}
    \sum_{k'=0}^{K-1} B^+_{l',k'}
    C_{k,k'}(r)
    \quad,
\end{align}
%
where
%
\begin{align}
    C_{k,k'}(r)
    &\equiv
    \frac{
        \exp\left(\frac{\vartheta_{k} - \vartheta_{k'}}{s}\right)
        \ln 
        \left(
            \frac{
                1+\exp\left(\frac{r -\Delta -\vartheta_{k}}{s}\right)
            }
            {
                1+\exp\left(\frac{r + \Delta -\vartheta_{k}}{s}\right)
            }
        \right)
        -
        \ln 
        \left(
            \frac{
                1+\exp\left(\frac{r -\Delta -\vartheta_{k'}}{s}\right)
            }
            {
                1+\exp\left(\frac{r + \Delta -\vartheta_{k'}}{s}\right)
            }
        \right)
    }{
        1
        -
        \exp\left(\frac{\vartheta_{k} - \vartheta_{k'}}{s}\right)
    }
    \quad.
\end{align}
%
In the limit $\Delta \rightarrow 0$,
%
\begin{align}
    \lim_{\Delta \rightarrow 0}
    \mathbf{E}_r
    &=
    \mathbf{B}^+ \mathbf{b}(r) \mathbf{b}^\top(r) {\mathbf{B}^+}^\top
    \quad.
\end{align}
%

@@

    {\mathbf{E}^l_r}^\top \,

@@

    {\mathbf{E}^l_r}^\top

@@

\subsubsection{Second moment}
%
We write the second moment integral as
%
\begin{proof}{}
    \mathbf{E}_\lambda
    & \equiv
    \int
    \mathbf{R}_{\hat{\mathbf{y}}}(\lambda) \,
    \mathbf{E}_\phi \,
    \mathbf{E}_\phi^\top \,
    \mathbf{R}_{\hat{\mathbf{y}}}^\top(\lambda) \,
    p(\lambda \, \big| \, \pmb{\theta}_{\lambda}) \,
    \mathrm{d}\lambda
    \nonumber
    \\
    %
    & =
    %
    \setstackgap{L}{1.25\baselineskip}
    \fixTABwidth{T}
    \parenMatrixstack{
    \mathbf{E}_\lambda^{0,0} & \mathbf{E}_\lambda^{0,1} & \mathbf{E}_\lambda^{0,2} & \cdots & \mathbf{E}_\lambda^{0,l_{\mathrm{max}}} \\
    \mathbf{E}_\lambda^{1,0} & \mathbf{E}_\lambda^{1,1} & \mathbf{E}_\lambda^{1,2} & \cdots & \mathbf{E}_\lambda^{1,l_{\mathrm{max}}} \\
    \mathbf{E}_\lambda^{2,0} & \mathbf{E}_\lambda^{2,1} & \mathbf{E}_\lambda^{2,2} & \cdots & \mathbf{E}_\lambda^{2,l_{\mathrm{max}}} \\
    \vdots & \vdots & \vdots & \ddots & \vdots \\
    \mathbf{E}_\lambda^{l_{\mathrm{max}},0} & \mathbf{E}_\lambda^{l_{\mathrm{max}},1} & \mathbf{E}_\lambda^{l_{\mathrm{max}},2} & \cdots & \mathbf{E}_\lambda^{l_{\mathrm{max}},l_{\mathrm{max}}}
    }
    \quad,
\end{proof}
%
where
%
\begin{proof}{}
    \mathbf{E}_\lambda^{l,l'}
    & =
    \int
    \mathbf{R}^l_{\hat{\mathbf{y}}}(\lambda) \,
    \mathbf{E}^l_\phi \,
    {\mathbf{E}^l_\phi}^\top \,
    {\mathbf{R}^{l'}_{\hat{\mathbf{y}}}}^\top(\lambda) \,
    p(\lambda \, \big| \, \pmb{\theta}_{\lambda}) \,
    \mathrm{d}\lambda
    \nonumber \\
    %
    & =
    %
    {\mathbf{U}^l}^{-1}
    \mathbf{P}^l_\lambda
    {{\mathbf{U}^l}^{-1}}^\top
\end{proof}
%
and we define
%
\begin{align}
    \label{eq:Pllam}
    \mathbf{P}^l_\lambda
     & \equiv
    \int
    \mathbf{D}^l_{\hat{\mathbf{x}}}(\lambda) \,
    \bar{\mathbf{E}}^l_\phi \,
    {\mathbf{D}^l_{\hat{\mathbf{x}}}}^\top(\lambda) \,
    p(\lambda \, \big| \, \pmb{\theta}_{\lambda}) \,
    \mathrm{d}\lambda
    \\
    \bar{\mathbf{E}}^l_\phi
     & \equiv
    \mathbf{U}^l
    \mathbf{E}^l_\phi
    {\mathbf{E}^l_\phi}^\top
    {\mathbf{U}^l}^\top
    \quad.
\end{align}
%
We then express the terms of $\mathbf{P}^l_\lambda$ as
%
\begin{align}
    {P^l_\lambda}_{m,m'}
     & =
    \int
    \sum\limits_{\mu=-l}^l
    \sum\limits_{\nu=-l}^l
    {D^l_{\hat{\mathbf{x}}}}_{m,\mu}(\lambda) \,
    {\bar{E}^l}{{}_\phi}_{\mu,\nu} \,
    {D^l_{\hat{\mathbf{x}}}}_{\nu,m'}(\lambda) \,
    p(\lambda \, \big| \, \pmb{\theta}_{\lambda}) \,
    \mathrm{d}\lambda
    %
    \nonumber \\[0.5em]
    %
     & =
    \sum\limits_{\mu=-l}^l
    \sum\limits_{\nu=-l}^l
    {\bar{E}^l}{{}_\phi}_{\mu,\nu}
    \sum\limits_{i=0}^{2l}
    \sum\limits_{j=0}^{2l}
    c_{m,\mu,i}^{l}
    c_{\nu,m',j}^{l}
    \,
    {Q^l_\lambda}_{i,j}
    \quad,
\end{align}
%
where
%
\begin{proof}{}
    {Q^l_\lambda}_{i,j}
    & \equiv
    \frac{1}{2\pi}
    \int_{-\pi}^{\pi}
    %
    \mathrm{sgn}(\sin\lambda)^{i+j}
    (1 - \cos\lambda)^{2l - \frac{i+j}{2}}
    (1 + \cos\lambda)^\frac{i+j}{2}
    %
    \,
    \mathrm{d}\lambda
    \nonumber \\[0.5em]
    %
    & =
    %
    \begin{cases}
        \dfrac{2^{2l} \Gamma \left(\frac{1+i+j}{2}\right)
            \Gamma \left(2l+\frac{1-i-j}{2}\right)}{\pi  \Gamma (2l+1)}
        %
         & i+j \,\, \mathrm{even}
        %
        \\
        %
        0
        %
         & i+j \,\, \mathrm{odd} \quad,
    \end{cases}
\end{proof}
%
whose terms may again be computed by upward recursion.

\section{The Contrast Integral}
\label{sec:contrast}
%
\xxx{Coming soon.}

\bibliography{bib}
\end{document}

>>>>

@@

@@

@@

\subsection{Probability density function}
%
For simplicity, we will adopt a uniform probability distribution for the
spot radius, characterized by a mean radius $r_0$ and a half-width $\Delta$:
%
\begin{align}
    p(r \, \big| \, \pmb{\theta}_{r})
     & =
    \begin{cases}
        \frac{1}{2\Delta} & r_0 - \Delta \leq r \leq r_0 + \Delta
        \\
        0                 & \mathrm{otherwise}
        \quad,
    \end{cases}
\end{align}
%
where the hyperparameters of the distribution are
%
\begin{align}
    \pmb{\theta}_r = \left(
    r_0 \, \, \, \,
    \Delta \right)^\top
    \quad.
\end{align}
%
As we argue in the text, in practice it is often difficult to constrain the
moments of the radius distribution above the first (the mean). It is
therefore useful to also consider the limiting case of the radius distribution
as $\Delta \rightarrow 0$, in which case the PDF becomes
%
\begin{align}
    p(r \, \big| \, \pmb{\theta}_{r}, \Delta = 0)
     & =
    \delta(r - r_0)
    \quad,
\end{align}
%
where $\delta$ is the delta function.
%

\subsection{First moment}
%
The first moment of the radius distribution is (Equation~\ref{eq:e1})
%
\begin{align}
    \mathbf{e}_r
     & \equiv
    \int
    \mathbf{s}(r) \,
    p(r \, \big| \, \pmb{\theta}_{r}) \,
    \mathrm{d}r
    \nonumber \\
     & =
    \frac{1}{2\Delta}
    \int_{r_0 - \Delta}^{r_0 + \Delta}
    \mathbf{s}(r) \,
    \mathrm{d}r
    \quad.
\end{align}
%
Using the equations from the previous section, its components may be written
%
\begin{align}
    (e_r)^l_m
     & =
    \frac{\delta_{m,0}}{2\Delta}
    \int_{r_0 - \Delta}^{r_0 + \Delta}
    \tilde{s}_{l}(r) \,
    \mathrm{d}r
    \nonumber \\
     & =
    \frac{\delta_{m,0}}{2\Delta}
    \sum_{k=0}^{K-1} B^+_{l,k}
    \int_{r_0 - \Delta}^{r_0 + \Delta}
    b_{k}(r)
    \mathrm{d}r
    \nonumber \\
     & =
    \frac{\delta_{m,0} s}{2\Delta}
    \sum_{k=0}^{K-1} B^+_{l,k}
    \ln
    \left(
    \frac{
        1+\exp\left(\frac{r -\Delta -\vartheta_k}{s}\right)
    }
    {
        1+\exp\left(\frac{r + \Delta -\vartheta_k}{s}\right)
    }
    \right)
    \quad.
\end{align}
%
In the limit $\Delta \rightarrow 0$,
%
\begin{align}
    \lim_{\Delta \rightarrow 0}
    \mathbf{e}_r
     & =
    \mathbf{B}^+ \mathbf{b}(r)
    \quad.
\end{align}
%

\subsection{Second moment}
%
The second moment of the radius distribution is (Equation~\ref{eq:E1})
%
\begin{align}
    \mathbf{E}_r
     & \equiv
    \int
    \mathbf{s}(r) \,
    \mathbf{s}^\top(r) \,
    p(r \, \big| \, \pmb{\theta}_{r}) \,
    \mathrm{d}r
    \nonumber \\
     & =
    \frac{1}{2\Delta}
    \int_{r_0 - \Delta}^{r_0 + \Delta}
    \mathbf{s}(r) \,
    \mathbf{s}^\top(r) \,
    \mathrm{d}r
    \quad.
\end{align}
%
As before, its components may be written
%
%
\begin{align}
    (E_r)^{l,l'}_{m,m'}
     & =
    \frac{\delta_{m,0}\delta_{m',0}}{2\Delta}
    \int_{r_0 - \Delta}^{r_0 + \Delta}
    \tilde{s}^l_{m}(r) \,
    \tilde{s}^{l'}_{m'}(r) \,
    \mathrm{d}r
    \nonumber \\
     & =
    \frac{\delta_{m,0}\delta_{m',0}}{2\Delta}
    \sum_{k=0}^{K-1} B^+_{l,k}
    \sum_{k'=0}^{K-1} B^+_{l',k'}
    \int_{r_0 - \Delta}^{r_0 + \Delta}
    b_{k}(r)
    b_{k'}(r)
    \mathrm{d}r
    \nonumber \\
     & =
    \frac{\delta_{m,0}\delta_{m',0}s}{2\Delta}
    \sum_{k=0}^{K-1} B^+_{l,k}
    \sum_{k'=0}^{K-1} B^+_{l',k'}
    C_{k,k'}(r)
    \quad,
\end{align}
%
where
%
\begin{align}
    C_{k,k'}(r)
     & \equiv
    \frac{
        \exp\left(\frac{\vartheta_{k} - \vartheta_{k'}}{s}\right)
        \ln
        \left(
        \frac{
            1+\exp\left(\frac{r -\Delta -\vartheta_{k}}{s}\right)
        }
        {
            1+\exp\left(\frac{r + \Delta -\vartheta_{k}}{s}\right)
        }
        \right)
        -
        \ln
        \left(
        \frac{
            1+\exp\left(\frac{r -\Delta -\vartheta_{k'}}{s}\right)
        }
        {
            1+\exp\left(\frac{r + \Delta -\vartheta_{k'}}{s}\right)
        }
        \right)
    }{
        1
        -
        \exp\left(\frac{\vartheta_{k} - \vartheta_{k'}}{s}\right)
    }
    \quad.
\end{align}
%
In the limit $\Delta \rightarrow 0$,
%
\begin{align}
    \lim_{\Delta \rightarrow 0}
    \mathbf{E}_r
     & =
    \mathbf{B}^+ \mathbf{b}(r) \mathbf{b}^\top(r) {\mathbf{B}^+}^\top
    \quad.
\end{align}
%

@@

@@

@@

\subsubsection{Second moment}
%
We write the second moment integral as
%
\begin{proof}{}
    \mathbf{E}_\lambda
    & \equiv
    \int
    \mathbf{R}_{\hat{\mathbf{y}}}(\lambda) \,
    \mathbf{E}_\phi \,
    \mathbf{R}_{\hat{\mathbf{y}}}^\top(\lambda) \,
    p(\lambda \, \big| \, \pmb{\theta}_{\lambda}) \,
    \mathrm{d}\lambda
    \nonumber
    \\
    %
    & =
    %
    \setstackgap{L}{1.25\baselineskip}
    \fixTABwidth{T}
    \parenMatrixstack{
    \mathbf{E}_\lambda^{0,0} & \mathbf{E}_\lambda^{0,1} & \mathbf{E}_\lambda^{0,2} & \cdots & \mathbf{E}_\lambda^{0,l_{\mathrm{max}}} \\
    \mathbf{E}_\lambda^{1,0} & \mathbf{E}_\lambda^{1,1} & \mathbf{E}_\lambda^{1,2} & \cdots & \mathbf{E}_\lambda^{1,l_{\mathrm{max}}} \\
    \mathbf{E}_\lambda^{2,0} & \mathbf{E}_\lambda^{2,1} & \mathbf{E}_\lambda^{2,2} & \cdots & \mathbf{E}_\lambda^{2,l_{\mathrm{max}}} \\
    \vdots & \vdots & \vdots & \ddots & \vdots \\
    \mathbf{E}_\lambda^{l_{\mathrm{max}},0} & \mathbf{E}_\lambda^{l_{\mathrm{max}},1} & \mathbf{E}_\lambda^{l_{\mathrm{max}},2} & \cdots & \mathbf{E}_\lambda^{l_{\mathrm{max}},l_{\mathrm{max}}}
    }
    \quad,
\end{proof}
%
where
%
\begin{proof}{}
    \mathbf{E}_\lambda^{l,l'}
    & =
    \int
    \mathbf{R}^l_{\hat{\mathbf{y}}}(\lambda) \,
    \mathbf{E}^l_\phi \,
    {\mathbf{R}^{l'}_{\hat{\mathbf{y}}}}^\top(\lambda) \,
    p(\lambda \, \big| \, \pmb{\theta}_{\lambda}) \,
    \mathrm{d}\lambda
    \nonumber \\
    %
    & =
    %
    {\mathbf{U}^l}^{-1}
    \mathbf{P}^l_\lambda
    {{\mathbf{U}^l}^{-1}}^\top
\end{proof}
%
and we define
%
\begin{align}
    \label{eq:Pllam}
    \mathbf{P}^l_\lambda
     & \equiv
    \int
    \mathbf{D}^l_{\hat{\mathbf{x}}}(\lambda) \,
    \bar{\mathbf{E}}^l_\phi \,
    {\mathbf{D}^l_{\hat{\mathbf{x}}}}^\top(\lambda) \,
    p(\lambda \, \big| \, \pmb{\theta}_{\lambda}) \,
    \mathrm{d}\lambda
    \\
    \bar{\mathbf{E}}^l_\phi
     & \equiv
    \mathbf{U}^l
    \mathbf{E}^l_\phi
    {\mathbf{U}^l}^\top
    \quad.
\end{align}
%
We then express the terms of $\mathbf{P}^l_\lambda$ as
%
\begin{align}
    {P^l_\lambda}_{m,m'}
     & =
    \int
    \sum\limits_{\mu=-l}^l
    \sum\limits_{\nu=-l}^l
    {D^l_{\hat{\mathbf{x}}}}_{m,\mu}(\lambda) \,
    {\bar{E}^l}{{}_\phi}_{\mu,\nu} \,
    {D^l_{\hat{\mathbf{x}}}}_{\nu,m'}(\lambda) \,
    p(\lambda \, \big| \, \pmb{\theta}_{\lambda}) \,
    \mathrm{d}\lambda
    %
    \nonumber \\[0.5em]
    %
     & =
    \sum\limits_{\mu=-l}^l
    \sum\limits_{\nu=-l}^l
    {\bar{E}^l}{{}_\phi}_{\mu,\nu}
    \sum\limits_{i=0}^{2l}
    \sum\limits_{j=0}^{2l}
    c_{m,\mu,i}^{l}
    c_{\nu,m',j}^{l}
    \,
    {Q^l_\lambda}_{i,j}
    \quad,
\end{align}
%
where
%
\begin{proof}{}
    {Q^l_\lambda}_{i,j}
    & \equiv
    \frac{1}{2\pi}
    \int_{-\pi}^{\pi}
    %
    \mathrm{sgn}(\sin\lambda)^{i+j}
    (1 - \cos\lambda)^{2l - \frac{i+j}{2}}
    (1 + \cos\lambda)^\frac{i+j}{2}
    %
    \,
    \mathrm{d}\lambda
    \nonumber \\[0.5em]
    %
    & =
    %
    \begin{cases}
        \dfrac{2^{2l} \Gamma \left(\frac{1+i+j}{2}\right)
            \Gamma \left(2l+\frac{1-i-j}{2}\right)}{\pi  \Gamma (2l+1)}
        %
         & i+j \,\, \mathrm{even}
        %
        \\
        %
        0
        %
         & i+j \,\, \mathrm{odd} \quad,
    \end{cases}
\end{proof}
%
whose terms may again be computed by upward recursion.

\section{The Contrast Integral}
\label{sec:contrast}
%
The final integrals we must take in our computation of
$\pmb{\mu}_{\mathbf{y}}(\pmb{\theta})$
amd $\pmb{\Sigma}_{\mathbf{y}}(\pmb{\theta})$ are the integrals over
the spot contrast distribution, $\mathbf{e}_c$ and $\mathbf{E}_c$.
These are by far the easiest, since the spot contrast is a scalar
multiplier of the spherical harmonic coefficient vector, so we can
pull the terms $\mathbf{e}_\lambda$ and $\mathbf{E}_\lambda$ out
of the
integrals in Equations (\ref{eq:e4}) and (\ref{eq:E4}) to write
%
\begin{align}
    \mathbf{e}_c
     & \equiv
    \mathbf{e}_\lambda \,
    \int
    c \,
    p(c \, \big| \, \pmb{\theta}_{c}) \,
    \mathrm{d}c
    \\
    \mathbf{E}_c
     & \equiv
    \mathbf{E}_\lambda \,
    \int
    c^2 \,
    p(c \, \big| \, \pmb{\theta}_c)
    \mathrm{d}c
    \quad.
\end{align}
%
These integrals may be computed analytically for any choice of
probability density function $p(c \, \big| \, \pmb{\theta}_c)$
with closed-form moments.
%
However, in practice, it is quite difficult to constrain the
spot contrast from light curves, let alone higher moments of its
distribution; this is due largely to the fact that the contrast $c$
is extremely degenerate with the total number of spots $N$
(see \S\ref{sec:cN-degeneracy}).
%
In our imeplementation of the algorithm,
we therefore choose the simplest possible probability distribution,
a delta function:
%
\begin{align}
    p(c \, \big| \, \pmb{\theta}_{c}) = \delta(c - c_0)
\end{align}
%
characterized by a single parameter, the contrast of the spots:
%
\begin{align}
    \pmb{\theta}_c = \left( c_0 \right)^\top
    \quad.
\end{align}
%
The moment integrals are then trivial to evaluate:
%
\begin{align}
    \mathbf{e}_c & = c \, \mathbf{e}_\lambda
    \\
    \mathbf{E}_c & = c^2 \mathbf{E}_\lambda
    \quad.
\end{align}
%
\bibliography{bib}
\end{document}
